Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
passive

Again we can define the loss we have observed in the sample used to estimate $\hat\theta$ [@sochLawUnconsciousStatistician2020]:
\begin{equation}
\mathbb{E}_y L(y, g(y|\hat\theta(y)))
 = \frac{1}{n}\sum_{i=1}^n L(y_i, g(y_i|\hat\theta(y)))
\end{equation}

However, what we are interested in is not how well the theory did on data that informed it but on future, yet unseen, data:
\begin{equation}
\mathbb{E}_x\mathbb{E}_yL(x, g(x|\hat\theta(y)))
\end{equation}
This expectation over, what is often called training and test data, is termed generalization error or expected prediction error [@bengioNoUnbiasedEstimator2004].
Note that both training ($y$) and test ($x$) data vary in this expectation.
Therefore, it is closely related to the expectation over data shown in Eq.\ \@ref(eq:dataexp) in the information-theoretic setup [@stoneAsymptoticEquivalenceChoice1977].

>>>>

Again the loss observed in the sample used to estimate $\hat\theta$ [@sochLawUnconsciousStatistician2020] can be defined:
\begin{equation}
\mathbb{E}_y L(y, g(y|\hat\theta(y)))
 = \frac{1}{n}\sum_{i=1}^n L(y_i, g(y_i|\hat\theta(y)))
\end{equation}

However, it is not of interest how well the theory did on data that informed it but on future, yet unseen, data:
\begin{equation}
\mathbb{E}_x\mathbb{E}_yL(x, g(x|\hat\theta(y)))
\end{equation}
This expectation over, what is often called training and test data, is termed generalization error or expected prediction error [@bengioNoUnbiasedEstimator2004].
Note that both training ($y$) and test ($x$) data vary in this expectation.
Therefore, it is closely related to the expectation over data shown in Eq.\ \@ref(eq:dataexp) in the information-theoretic setup [@stoneAsymptoticEquivalenceChoice1977].
